---
title: "03_gca"
author: "Lena V. Kremin"
output: html_notebook
---

This notebook contains the growth curve analysis of CompMix-36 combining Montreal and Princeton data. Must be run after 02_looking-time_analysis

# Prep script

##load packages

```{r}
library(tidyverse)
library(lme4)
library(lmerTest)

library(devtools)

library(here)

#Workaround since gazer does not seem to be on R Jan 5, 2023. Install from github
#devtools::install_github("dmirman/gazer")
library(gazer)
```

## load data

``` {r}
# load data

## Keepers
msl_keepers <- read_csv("data_frames/msl_keepers.csv") 

## eye tracking data - time course

gca_df <- read_csv("data_frames/gaze_trial_time_gca.csv", col_types = cols(study_id = col_character()))


## gaze target df

gaze_target <- read_csv(here("data_frames/gaze_target_sum.csv")) %>% 
  mutate(trial_type = as.factor(trial_type),
         location = as.factor(testing_location))


```

# Growth Curve Analysis

## create ordered polynomials

```{r}
##### followed instructions/tutorial from https://dmirman.github.io/GCA/TargetFix_example.html

### create df for gca

# filter for only target looks
gca_df <- gca_df %>% 
  filter(AOI == "target_look")

# create 2nd order orthogonal polynomial
gca <- code_poly(gca_df, predictor = "Time", poly.order = 2, orthogonal = TRUE) %>% 
  mutate(study_id = as.factor(study_id),
         trial_type = as.factor(trial_type),
         testing_location = as.factor(testing_location),
         study_lang_dom = as.factor(study_lang_dom))

contrasts(gca$trial_type) <- contr.helmert(2)/2
contrasts(gca$testing_location) <- contr.helmert(2)/2
contrasts(gca$study_lang_dom) <- contr.helmert(2)/2

write_csv(gca, "data_frames/growth_curve_analysis.csv")
save(gca, file = here("data_frames/growth_curve_analysis.Rda"))


```

## fit models

### base model
``` {r}

## fit base model - linear and quadratic time only
model_base <- lmer(Prop ~ (poly1+poly2) + (poly1+poly2  || study_id), 
               data=gca, REML=F)
summary(model_base)


## add effect of trial type
model_type <- lmer(Prop ~ (poly1+poly2) + trial_type + (poly1+poly2  || study_id), 
               data=gca, REML=F)
summary(model_type)

anova(model_base, model_type)
# sig improvement


## add effect of trial type on slope
model_type_slope <- lmer(Prop ~ (poly1+poly2) + trial_type + trial_type:poly1 + (poly1+poly2  || study_id), 
               data=gca, REML=F)
summary(model_type_slope)

anova(model_type, model_type_slope)
# doesn't significantly improve model, so remove trial_type:slope
```

### location model
``` {r}
# ## add testing location (ME & interaction)
model_type_location <- lmer(Prop ~ (poly1+poly2) + trial_type * testing_location + (poly1+poly2  || study_id),
               data=gca, REML=F)
summary(model_type_location)

anova(model_type, model_type_location)
# loc sig improves model


# ## add testing location for slope
model_type_location_slope <- lmer(Prop ~ (poly1+poly2) + trial_type * testing_location + testing_location:poly1 + (poly1+poly2  || study_id),
               data=gca, REML=F)
summary(model_type_location_slope)

anova(model_type_location, model_type_location_slope)
#  sig improves model

# ## add testing location for quadratic
model_type_location_quadratic <- lmer(Prop ~ (poly1+poly2) + trial_type * testing_location + testing_location:poly1 + testing_location:poly2 + (poly1+poly2  || study_id),
               data=gca, REML=F)
summary(model_type_location_quadratic)

anova(model_type_location_slope, model_type_location_quadratic)
#  sig improves model




# add trial type as random slope
model_type_location_ran_slope <- lmer(Prop ~ (poly1+poly2) + trial_type * testing_location + testing_location:poly1 + testing_location:poly2 + ((poly1+poly2) + trial_type || study_id), 
               data=gca, REML=F)
summary(model_type_location_ran_slope)
# model fails to converge

##### select model_type_location_quadratic as final model #####



## This model tells us that effect of trial type on intercept is not statistically significant (replicates results of t-tests).  
## intercept - value when all predictors are 0
## linear term - y increases over time
## quadratic term - curve grows then drops
## trial_type - no ME, single language not lowered compared to mixed
## location - no ME, overall kids do equally as well across locations
## trial_type : location - kids in princeton do worse on single language trials
## linear : location - princeton kids have reduced slope, orientation to target not as quick
## quadratic : location - stronger peak?
```

### SES model
``` {r}
## add SES (ME & interaction)
model_type_ses <- lmer(Prop ~ (poly1+poly2) + trial_type * edu_years + (poly1+poly2  || study_id), data=gca, REML=F)
summary(model_type_ses)

anova(model_type, model_type_ses)

## add SES as slope - FINAL SES MODEL
model_type_ses_slope <- lmer(Prop ~ (poly1+poly2) + trial_type * edu_years + edu_years:poly1 + (poly1+poly2  || study_id), data=gca, REML=F)
summary(model_type_ses_slope)

anova(model_type_ses, model_type_ses_slope)

## add SES as quadratic
model_type_ses_quad <- lmer(Prop ~ (poly1+poly2) + trial_type * edu_years + edu_years:poly1 + edu_years:poly2 + (poly1+poly2  || study_id), data=gca, REML=F)
summary(model_type_ses_quad)

anova(model_type_ses_slope, model_type_ses_quad)
# almost but not quite significantly improves model

## as trial type as random slope
model_type_ses_ran_slope <- lmer(Prop ~ (poly1+poly2) + trial_type * edu_years + edu_years:poly1 + ((poly1+poly2) + trial_type  || study_id), data=gca, REML=F)
summary(model_type_ses_ran_slope)
#fails to converge

#trying to understand ses x trial type interaction 
gaze_target_wide <- gaze_target %>% 
  pivot_wider(id_cols = c("study_id", "edu_years"), names_from = "trial_type", values_from = "Prop") %>% 
  mutate(diff = Single - Mixed )


ggplot(filter(gaze_target, edu_years > 10), aes(x = edu_years, y = Prop, color = testing_location)) +
  geom_point() + 
  geom_smooth(method = 'lm') +
  facet_grid(. ~ trial_type)

```
### vocab model

```{r}
# redo model_type to match S's with vocab score (S13 missing)
model_type_mod <- lmer(Prop ~ (poly1+poly2) + trial_type + (poly1+poly2  || study_id), data= filter(gca, study_id != "S13"), REML=F)
summary(model_type_mod)


## add vocab (ME & interaction) - final vocab model
## all it says is that performance improves with higher vocab, no interaction w trial type
model_type_vocab <- lmer(Prop ~ (poly1+poly2) + trial_type * vocab_total + (poly1+poly2  || study_id), data=filter(gca, study_id != "S13"), REML=F)
summary(model_type_vocab)

anova(model_type_mod, model_type_vocab)

## vocab as slope - fails to converge
model_type_vocab_slope <- lmer(Prop ~ (poly1+poly2) + trial_type * vocab_total + vocab_total:poly1 + (poly1+poly2  || study_id), data=filter(gca, study_id != "S13"), REML=F)
summary(model_type_vocab_slope)
```


### dominance model

```{r}
## add dominance (ME & interaction) - does not significantly improve model
model_type_dom <- lmer(Prop ~ (poly1+poly2) + trial_type * study_lang_dom + (poly1+poly2  || study_id), data=gca, REML=F)
summary(model_type_dom)

anova(model_type, model_type_dom)
```
### lang_mix model

```{r}
## add dominance (ME & interaction) - does not significantly improve model
model_type_lang_mix <- lmer(Prop ~ (poly1+poly2) + trial_type * lang_mix + (poly1+poly2  || study_id), data=gca, REML=F)
summary(model_type_lang_mix)

# significant interaction between trial type and language mixing

anova(model_type, model_type_lang_mix)

# note that lang_mix doesn't significantly improve model fit compared to base model. Will still explore these results, but no justification to report this model.


## add lang_mix as slope FINAL LANG_MIX MODEL
model_type_lang_mix_slope <- lmer(Prop ~ (poly1+poly2) + trial_type * lang_mix + lang_mix:poly1 + (poly1+poly2  || study_id), data=gca, REML=F)
summary(model_type_lang_mix_slope)

anova(model_type_lang_mix, model_type_lang_mix_slope) #no sign. improvement


## add lang_mix as quadratic
model_type_lang_mix_quad <- lmer(Prop ~ (poly1+poly2) + trial_type * lang_mix + lang_mix:poly1 + lang_mix:poly2 + (poly1+poly2  || study_id), data=gca, REML=F)
summary(model_type_lang_mix_quad)

anova(model_type_lang_mix_slope, model_type_lang_mix_quad) # no sign. improvement


## as trial type as random slope
model_type_lang_mix_ran_slope <- lmer(Prop ~ (poly1+poly2) + trial_type * lang_mix + lang_mix:poly1 + ((poly1+poly2) + trial_type  || study_id), data=gca, REML=F)
summary(model_type_lang_mix_ran_slope)
# Fails to converge


#trying to understand lang_mix x trial type interaction (even though overall model is not significantly better than null model)
#seems to go back to Montreal-Princeton difference we identified in other analyses
gaze_target_wide_lang_mix <- gaze_target %>% 
  pivot_wider(id_cols = c("study_id", "lang_mix"), names_from = "trial_type", values_from = "Prop") %>% 
  mutate(diff = Single - Mixed )

ggplot(filter(gaze_target, lang_mix > 15), aes(x = lang_mix, y = Prop, color = trial_type)) +
  geom_point() + 
  geom_smooth(method = 'lm')

ggplot(filter(gaze_target, lang_mix > 15), aes(x = lang_mix, y = Prop, color = trial_type)) +
  geom_point() + 
  geom_smooth(method = 'lm')+
  facet_grid(.~testing_location)


```



## plot model

### base model
```{r}
## set up a data frame to predict values for: one row per participant/cond label pair
newdata_base <- gca %>% 
  select(study_id, trial_type, Time, testing_location, Prop, poly1, poly2)

newdata_base <- newdata_base %>% 
  ## get the predicted value for each case
  mutate(pred = predict(model_type, newdata=newdata_base))


ggplot(newdata_base, aes(x = Time, y = Prop, color = trial_type)) + 
  stat_summary(aes(y = Prop, shape = trial_type), fun.data=mean_se, geom="pointrange", size = .75) + 
  stat_summary(aes(y = pred), fun=mean, geom="line", size = 0.75) +
  expand_limits(y=c(0.5, 1)) +
  scale_color_manual(labels = c("Code-Switched", "Single Language"),
                     values = c("#1f78b4", "#33a02c"),
                     name = "Trial Type") +
  scale_shape_manual(labels = c("Code-Switched", "Single Language"),
                     values = c(19, 15),
                     name = "Trial Type") +
  labs(x = "Time from Noun Onset", y = "Proportion Looking to Target") +
  theme(legend.text = element_text(size = 12),
        legend.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        axis.title.y = element_text(margin = margin(r = 14)),
        strip.text.x = element_text(size = 12))
```


### location model

``` {r}
## set up a data frame to predict values for: one row per participant/cond label pair
newdata <- gca %>% 
  select(study_id, trial_type, Time, testing_location, Prop, poly1, poly2)

newdata <- newdata %>% 
  ## get the predicted value for each case
  mutate(pred = predict(model_type_location_quadratic, newdata=newdata))



# viz showing model predicted time courses for individual participants 
ggplot(newdata, aes(x = Time, y = pred, color = testing_location, linetype = trial_type)) +
    geom_smooth() +
  facet_wrap(~ study_id, ncol = 5)

ggsave("figures/growth_curve_analysis_predictions.png", width = 8.4, height = 6.9, dpi = 500)





ggplot(newdata, aes(x = Time, y = Prop, color = trial_type)) + 
  stat_summary(aes(y = Prop, shape = trial_type), fun.data=mean_se, geom="pointrange", size = .75) + 
  stat_summary(aes(y = pred), fun=mean, geom="line", size = 0.75) +
  expand_limits(y=c(0.5, 1)) +
  scale_color_manual(labels = c("Code-Switched", "Single Language"),
                     values = c("#1f78b4", "#33a02c"),
                     name = "Trial Type") +
  scale_shape_manual(labels = c("Code-Switched", "Single Language"),
                     values = c(19, 15),
                     name = "Trial Type") +
  labs(x = "Time from Noun Onset", y = "Proportion Looking to Target") +
  facet_grid(. ~ testing_location, labeller = as_labeller(c("Montreal" = "Canada", "Princeton" = "United States")))  +
    theme(legend.text = element_text(size = 12),
          legend.title = element_text(size = 14),
          axis.text = element_text(size = 12),
          axis.title = element_text(size = 14),
          axis.title.y = element_text(margin = margin(r = 14)),
          strip.text.x = element_text(size = 12))


ggsave("figures/growth_curve_analysis_bucld.png", width = 11, height = 6.9, dpi = 500)



```


### SES model

```{r}
## set up a data frame to predict values for: one row per participant/cond label pair
newdata_ses <- gca %>% 
  select(study_id, trial_type, Time, testing_location, edu_years, Prop, poly1, poly2)

newdata_ses <- newdata_ses %>% 
  ## get the predicted value for each case
  mutate(pred = predict(model_type_ses_slope, newdata=newdata_ses))

ggplot(gaze_target, aes(x = edu_years, y = Prop, color = trial_type)) +
  geom_point() +
  geom_smooth(method = 'lm')

ses <- newdata_ses %>% 
  group_by(study_id, testing_location, edu_years) %>% 
  summarize(n = n()) %>% 
  group_by(edu_years, testing_location) %>% 
  summarize(n = n())

ggplot(newdata_ses, aes(x = Time, y = Prop, color = trial_type)) + 
  stat_summary(aes(y = Prop), fun.data=mean_se, geom="pointrange", size = .5) + 
  stat_summary(aes(y = pred), fun=mean, geom="line", size = 0.5) +
  expand_limits(y=c(0.5, 1)) +
  scale_color_manual(labels = c("Code-Switched", "Single Language"),
                     values = c("#1f78b4", "#33a02c"),
                     name = "Trial Type") +
  scale_shape_manual(labels = c("Code-Switched", "Single Language"),
                     values = c(19, 15),
                     name = "Trial Type") +
  labs(x = "Time from Noun Onset", y = "Proportion Looking to Target") +
  facet_grid(. ~ cut_interval(edu_years, 4), labeller = as_labeller(c(
    "[4,8.25]" = "4 - 8 years (N = 2)",
    "(8.25,12.5]" = "9 - 12 years (N = 5)",
    "(12.5,16.8]" = "13 - 16 years (N = 12)",
    "(16.8,21]" = "17 - 21 years (N = 11)")))  #+
    # theme(legend.text = element_text(size = 12),
    #       legend.title = element_text(size = 14),
    #       axis.text = element_text(size = 12),
    #       axis.title = element_text(size = 14),
    #       axis.title.y = element_text(margin = margin(r = 14)),
    #       strip.text.x = element_text(size = 12))
#all kids in lowest two groups are from PCT, 3rd all from MTL, last 7 from MTL, 4 from PCT

```


## Exploratory 

### GCA w dom

```{r}
# explore how lang dom may be affecting things
dom_type <- lmer(Prop ~ (poly1+poly2) + trial_type * study_lang_dom + (poly1+poly2  || study_id), 
               data=gca, REML=F)
summary(dom_type)

anova(model_type, dom_type)
# does not stat improve model


model_dom <- lmer(Prop ~ (poly1+poly2) + trial_type * testing_location + testing_location:poly1 + testing_location:poly2 + study_lang_dom + (poly1+poly2  || study_id),
               data=gca, REML=F)
summary(model_dom)

anova(model_dom, model_type_location_quadratic)


# look how model fits with only dom
gca_dom_only <- gca %>% 
  filter(study_lang_dom == "dom")

final_dom_only <- lmer(Prop ~ (poly1+poly2) + trial_type * testing_location + testing_location:poly1 + testing_location:poly2 + (poly1+poly2  || study_id),
               data=gca_dom_only, REML=F)
summary(final_dom_only)
# same pattern

# look for interaction
final_dom_int <- lmer(Prop ~ (poly1+poly2) + trial_type * testing_location + testing_location:poly1 + testing_location:poly2 + study_lang_dom:trial_type + (poly1+poly2  || study_id),
               data=gca, REML=F)
summary(final_dom_int)
#does not add anything as ME or interaction
```


## number of trials per time bin

```{r}
time_n <- gca_df %>% 
  filter(Prop != "NaN") %>% 
  group_by(Time, trial_type, testing_location) %>% 
  summarize(n_trials = n(),
            n_subjs = length(unique(study_id))) %>% 
  mutate(z_trials = n_trials/n_subjs)

time_n_avg <- time_n %>% 
  ungroup() %>% 
  group_by(testing_location, trial_type) %>% 
  summarize(avg_trials = mean(z_trials))

ggplot(time_n, aes(x = Time, y = z_trials, color = trial_type))+
  geom_point() +
  facet_grid(. ~ testing_location) +
  geom_hline(data = time_n_avg, aes(yintercept = avg_trials, color = trial_type))
```

